### 2011-01-16 docs/tex/review.tex
some more changes

\section{Introduction}
This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo \ref{holland1996} and other such simulated Complex Adaptive Systems. In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.

@@

\subsection{Evolutionary Algorithms}
Algorithms which are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generation, can be defined as evolutionary algorithms. There are many different forms of evolutionary algorithm. All of them can be generalized to follow their pattern from natural selection. The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual from the set of existing solution space. An individual or a solution which provides higher output from the fitness function is considered as more fit to survive in the environment. So given a problem the algorithm initializes the environment with a random set of population or solutions. Then it uses the fitness function to select a better set of solutions from the existing ones. After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set, born from the existing ones. Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.

@@

In regards to parent selection the most commonly used process by GA is fitness proportion selection, where the selection probability of a parent depends on the absolute fitness value of the individual compared to the absolute fitness values of the rest of the population. A fitness value is evaluated from the evaluation or the fitness function. Introduced by Holland \cite{holland1975} this procedure has a few problems. Premature convergence being one where individuals that are a lot better than the rest take over the entire population. Also when fitness values are all very close, there is almost no selection pressure in evolution of the fittest. Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection. This procedure preserves a constant selection pressure by sorting the population on the basis on fitness, and then allocating selection probabilities to individuals according to their rank. Both of the above mentioned selection procedures requires knowledge of the entire population. But when the population size is very large Tournament selection is an effective process \cite{eiben2003}. In this case a randomized pre-selection is done over the large population and then they are ranked according to their fitness value and selected as parent.

>>>>

\section{Introduction}
This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo \cite{holland1996} and other such simulated Complex Adaptive Systems. In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.

@@

\subsection{Evolutionary Algorithms}
Evolutionary algorithms are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generations. There are many different forms of evolutionary algorithm. All of them can be generalized to follow their pattern from natural selection. The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual from the set of existing solution space. An individual or a solution which provides higher output from the fitness function is considered as more fit to survive in the environment. So given a problem the algorithm initializes the environment with a random set of population or solutions. Then it uses the fitness function to select a better set of solutions from the existing ones. After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set, born from the existing ones. Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.

@@

In regards to parent selection the most commonly used process by GA is fitness proportion selection, where the selection probability of a parent depends on the absolute fitness value of the individual compared to the absolute fitness values of the rest of the population. A fitness value is evaluated from the evaluation or the fitness function. Introduced by Holland \cite{holland1975} this procedure has a few problems. Premature convergence being one where individuals that are a lot better than the rest take over the entire population. Also when fitness values are all very close, there is almost no selection pressure in evolution of the fittest. Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection. This procedure preserves a constant selection pressure by sorting the population on the basis of fitness, and then allocating selection probabilities to individuals according to their rank. Both of the above mentioned selection procedures requires knowledge of the entire population. But when the population size is very large Tournament selection is an effective process \cite{eiben2003}. In this case a randomized pre-selection is done over the large population and then they are ranked according to their fitness value and selected as parent.
